Creating optimal conditions for reproducible data analysis in \R with `fertile'\protect\thanks{The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the \pkg{tidyverse} team.}

### 2020-10-15 STAT-paper-template/APA/response-to-reviewers.md

This feature (version-specific dependency tracking) has been added to fertile since the original manuscript was submitted. A short section detailing the new functionality is now at the bottom of the existing section on project dependency management right after the code for proj_pkg_script().

*p. 10:  Too bad the pandemic interrupted your cool-sounding study!  It does seem that the study could be run in an online-only class environment though; is this true and is it worth mentioning?*

Yes, this is true! Since the submission of the original manuscript, we decided to conduct another trial in the classroom in fall 2020, now that Smith College is 100% online. The text has been updated to reflect this.

## Reviewer’s Comments

General:

*- the use of shims is likely unfamiliar to R users. Therefore, I have some concern about the ability of a user to control how aggressively this package performs. For example, if a user specifies an absolute path and receives an error message, it will be difficult for the user to determine what function was used to specify this error message and determine if there is a way to be less aggressive (to turn that into a warning, instead of an error, for example). My fear is that this functionality may limit use. However, I do like that the sandbox() function addresses this to an extent, allowing users to test things out and "get it right" before retuning to where the original error message was received.*

This is an excellent point! Part of the reason that fertile is so strict on this behavior is that in our experience, many R coders (particularly those with little experience) tend to ignore warnings as long as their code executes properly. Having fertile’s path-related behavior be error based ensures that no one will skip over the messages that come up. However, we do recognize that some users may still want to run these functions despite the warnings. In order to take this into account, we have added detail to the error messages produced by the shims. The new messages provide users with a strategy to override the error produced by fertile.

@@

- *Section 3.1: may be helpful to be very clear here that these are errors and not warnings. "catches" wasn't clear as to whether I would be allowed to specify an absolute path and would get a warning, or whether this would aggressively error. (Note: the code makes this clear, but the text may benefit from slight clarification).*

This has been clarified in the text. In addition, further explanation of the difference in response between the read.csv() and setwd() examples has been provided.

- *3.2 `list_checks()` is a nice function, but a table with the checks and a brief description of what that check does in the paper would be beneficial.*

This table has been added! Since `list_checks()` provides no additional benefit to the user than the information in this table, it is no longer mentioned.

@@

- *in 3.1 and 3.2, it may be nice to describe explicitly whether it's possible to just use one or the other (proactive vs retroactive)....similar to how in 3.3 it's described how logging can be turned off (or reset). I could envision one wanting to develop without error and then check at the end (retroactive only). Philosophically, I could see that you would not want to build that in and that people could then just load your package at the end...but this may be something explicitly stated in the manuscript.*

Thank you for pointing this out. A comment to this effect has been added to the end of the description of retroactive behavior.

- *Section 3.2: The average user may not know what the tidyselect helper functions are.  A bit more explanation here would likely help readers/users.*

A short description of tidy select helpers and their applicability here has been added just before the `proj_check_some()` example.

@@

- *Section 3.5.4: the line of code `cat(readChar(install_script, 1e5))` is not intuitive, and that line may benefit from a comment with a brief explanation within the code itself (or in the text above)*

That code has been hidden from view. Instead, there is now a sentence stating that we are looking into the contents of the file.

- *Section 4: Suggestion to rename to future directions or something other than results, given the lack of results here (no fault of the authors, here! simply beyond one's control.) But, I did read and was bummed to see no results here after the section header was Results. Excited to see these results in the future, regardless!*

Agreed on this point. No results are discussed so that warrants a name change. Since the section is about an experiment, however, we have chosen to replace it with “Experimental Testing”. We also decided to run a second trial this semester, so "future directions" is no longer an applicable name as it is happening currently!

### 2020-10-15 STAT-paper-template/APA/fertile.Rnw
changed sample shim to read.csv
added reference and edits

\textcolor{blue}{Users who want to override this behavior and execute their function anyway are provided with a snipped of code to execute that will achieve this for them.}

\pkg{fertile} is even more aggressive with functions (like \func{setwd}) that are almost certain to break reproducibility \textcolor{blue}{no matter the type of path passed to them}. \textcolor{red}{\st{, causing them to throw errors that prevent their execution and providing recommendations for better alternatives}}. \textcolor{blue}{When these functions are called, users are not presented with an option to override the resulting error. Instead, the only way to achieve the desired action is for the user to execute a different function that produces the same behavior but in a reproducible way.}

@@

\textcolor{blue}{Both the proactive and retroactive features available in \pkg{fertile} are enabled automatically upon the loading of the package. To prevent users from accidentally enabling or disabling features, \pkg{fertile} does not provide any option to control which features are active. However, those who want to use the proactive features can simply  refrain from using the retroactive-specific functions.
Conversely, those who want to use only the retroactive features can wait to load \pkg{fertile} until they are ready to produce a report on their project.}

>>>>

\textcolor{blue}{For users who want to override this behavior and execute their function anyway, we provide a snippet of code to bypass \pkg{fertile} and execute the original function call.}

\pkg{fertile} is even more aggressive with functions (like \func{setwd}) that are almost certain to break reproducibility \textcolor{blue}{no matter the type of path passed to them}. \textcolor{red}{\st{, causing them to throw errors that prevent their execution and providing recommendations for better alternatives}}. \textcolor{blue}{When these functions are called, users are not presented with an option to override the resulting error. Instead, the preferred way to achieve the desired action is for the user to execute a different function that produces the same behavior but in a reproducible way. For example, by using the \func{here} function from the \pkg{here} package \citep{R-here} instead of \func{setwd}.}

@@

\textcolor{blue}{Both the proactive and retroactive features available in \pkg{fertile} are enabled automatically upon loading the package. To prevent users from accidentally enabling or disabling features, \pkg{fertile} does not provide any option to control which features are active. However, those who want to use the proactive features can simply  refrain from using the retroactive-specific functions.
Conversely, those who want to use only the retroactive features can wait to load \pkg{fertile} until they are ready to produce a report on their project.}
